\documentclass[a4paper,10pt]{article}
\usepackage[]{graphicx}
\usepackage[]{times}
\usepackage{geometry}

\geometry{verbose,a4paper,tmargin=1.5cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\renewcommand{\baselinestretch}{1.0}

\title{TER user manual \\ \small (version 2.0 beta)}

\author{
GICI group \vspace{0.1cm} \\
\small Department of Information and Communications Engineering \\
\small Universitat Aut{\`o}noma Barcelona \\
\small http://www.gici.uab.es  -  http://www.gici.uab.es/TER \\
\small  http://sourceforge.net/projects/ter \\
}

\date{November 2007}

\begin{document}
\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
\label{sect:overview}

	
TER is an implementation of the CCSDS Recommendation for Image Data
Compression (Recommended Standard CCSDS 122.0-B-1 Blue Book). TER
implements not only the CCSDS Recommendation, but also new features
add to the Recommended Standard. TER is designed and programmed with
the aim to provide a good basis to test and develop the CCSDS
Recommendation for Image Data Compression. The application provides
different functionalitites that can be controlled via its
parameters. These parameters can be passed as program arguments,
selecting some of the algorithms that the application
incorporates. More than 30 parameters allow the combination of
different processes to produce a compressed image codestream. Each one
of these parameters and its valid arguments are explained in the
application help and in this manual. When added features are used, the
encoded file is not compilant with the Recommendation. Parameters employed in the added
features are also required as program arguments to correctly perform
the decoding process.

TER also defines a new file syntax for the Recommendation by adding
some embedded headers.
The features added by the new file syntax are similar to the ones
available in JPEG2000 and in JPIP.
As in JPEG2000, the encoded stream can be ordered by: quality (L),
position (P), resolution (R), and component (C);
obtaining, among others, the following progression orders: LRCP, RLCP,
RPCL, PCRL, and CPRL. Embedded headers permit to decode in any progression
order, even if the image was encoded using a different one. In addition,
TER allows to decorrelate in the spectral domain
before encoding the whole image instead each band separately
as restricted in the Recommendation.

A development manual is also available and the API is well documented
to facilitate an easy understanding, extension and modification of
the application. All the design and implementation details are widely
explained in these manuals and the source code is commented. All
these information is publicly available in the web page
http://www.gici.uab.es/TER, where you can download the sources and
the manuals. To guarantee a free distribution, TER has the General
Public License (GNU GPL) of the Free Software Foundation
(http://www.fsf.org/licensing/licenses/gpl.html).


TER incorparates algorithms to make it flexible enough to manage
different kind of data, to control and monitor the compression 
stages, to extract statistical information, etc. As we explained
above TER is a platform to test new ideas, not to be a commercial
product or to be integrated to other applications that need support
for encoding/decoding files compilant with the CCSDS Recommendation
for Image Data Coding. The double functionality of the application
makes that the application performance cannot be as good as some other
implementations, so for commercial purposes the GICI group does not
recommend the use of this application.

We have tried to make a good design and efforts have been made to
develop and implement the application as useful as
desirable. However, we could not foresee all the needs of TER
users, so we will thank you for all the suggestions and comments
that you can report to us (gici-dev@abra.uab.es). 

\flushright{We hope you enjoy it, \vspace{0.25cm}\\GICI
  group}\flushleft{} 

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Usage}
\label{sect:usage}

TER is divided in 3 applications: the encoder, the decoder
and, the extractor of images using the quality, postion,
component, and resolution scalability of a TER file. All
programs are encapsulated in jar files in the \emph{dist/}
directory and can be executed separately using the JVM. Each
application accepts its own parameters which can be passed as
simple command arguments, i.e. \emph{java -jar dist/TERcode.jar -i
  inputImage.pgm}. The distribution incorporates a shell script both 
for the encoder and the decoder called \emph{TERcode} and
\emph{TERdecode} to facilitate executions in a GNU/Linux
environment. TER may use a great amount of memory. Hence, it is
recommended to set the maximum amount of memory that the
application can allocate (usually the same as you computer RAM) via
the \emph{-Xmx} parameter of the JVM, i.e. \emph{java -Xmx512m -jar
  dist/TERcode.jar -i inputImage}.  


The usage of TER is very simple. To compress an image you can use
the encoder with some specific parameters. All the functionalities of
TER are explained with the application parameters, so 
it is recommended to read them to know what you can do. Do not
worry if you select incompatible parameters or functionalities; the
application detects these problems and displays warning messages to
the user. 

When you have a compressed codestream, you can use the decoder to
recover the original image and save it with other common
formats. TER decoder can manage codestreams compliant with the CCSDS
Recommendation for Image Data Coding generated by other
applications. However not all the options 
defined in the Recommended Standard are implemented. TER decoder can
also manage specific TER files not compilant with the Recommendation.
In such cases, it is required that the user indicates that the file is
not compilant and that passes to the decoder the parameters using by
the encoder as program parameters.

A typical use of the application is as follows: 

\hspace{0.5cm}\emph{\# TERcode -i lena.pgm -o lenaCompressed.ter} \\ 
\hspace{0.5cm}\emph{\# TERdecode -i lenaCompressed.ter -o
  lenaRecovered.pgm} \\  

or if you do not use the shell scripts:

\hspace{0.5cm}\emph{\# java -Xmx512m -jar dist/TERcode.jar -i
  lena.pgm -o lenaCompressed} \\ 
\hspace{0.5cm}\emph{\# java -Xmx512m -jar dist/TERdecode.jar -i
  lenaCompressed.ter -o lenaRecovered.pgm} \\  

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parameters}
\label{sect:parameters}

In this section all supported parameters both for the encoder and
the decoder are explained. This documentation is extracted from the
application help and it explains all the algorithms incorporated to
TER. By reading them you will know all the functionalities of the
application. 

Parameters have two formats: the long and the short
specification. Long specification has $-$$-$ at the beginning while
short specification has $-$ (it does not matter which one you
choose). Each parameter has its own arguments, which usually are
integers, floats, booleans (0 to indicate false and 1 to indicate
true) or strings. If the user specifies some invalid arguments, the
application will display warning messages. Most of these parameters
are not mandatory. When they are not specified default values are
used. The following table shows how each parameter will be
displayed in this manual: 

\begin{center}\begin{tabular}{|rr|rlrl|}
	 \hline
	 \multicolumn{2}{|l|}{\textbf{$-$$-$longParameter}} &
	 \multicolumn{4}{|l|}{$\{$parameter arguments$\}$} \\
	 \cline{3-6}
	 \multicolumn{2}{|l|}{\textbf{$-$shortParameter}} & \emph{Mandatory:} & Yes/No & &  \\
	 \hline
	 \emph{Explanation:} & \multicolumn{5}{|p{12cm}|}{Parameter explanation} \\
	 \hline
	 \emph{Default:} & \multicolumn{5}{|p{12cm}|}{Parameter default values.} \\
	 \hline
\end{tabular}\end{center}

\subsection{TERcoder parameters}
\label{sect:encoderParameters}

\input{coderParameters}

\newpage

\subsection{TERdecoder parameters}
\label{sect:decoderParameters}

\input{decoderParameters}

\newpage

\subsection{TERdisplay parameters}
\label{sect:displayParameters}

\input{displayParameters}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples}
\label{sect:examples}

\vspace{0.25cm}\textbf{LOSSLESS COMPRESSION USING A SINGLE SEGMENT}\vspace{0.25cm}  

\emph{\#TERcode -i workDir/mars512x32.raw -g 1 32 512 1 0 0 -of 0
  workDir/mars512x32} \\

This execution will generate a file (compilant with the
Recommendation) called \emph{mars512x32.rec}. The default mode of TER
is lossless compression using a single segment and employing part 2,3
and 4 flag for the segment. To decompress the file and recover the
original image run:

\emph{\#TERdecode -i workDir/mars512x32.rec -o
  workDir/mars512x32.ter.raw -g 1 32 512 1 0 0 } \\   

If the user wants to store the image in a known format, for example
'pgm' format, then there is not needed the geometry of the output
image. The user could run:

\emph{\# TERdecode -i workDir/mars512x32.rec -o
  workDir/mars512x32.ter.pgm} \\ 

\vspace{0.25cm}\textbf{LOSSLESS COMPRESSION USING MORE THAN ONE
  SEGMENT}\vspace{0.25cm}  
		
\emph{\#TERcode -i workDir/sar16bit.raw -g 1 512 512 2 0 0 -wt 4
  --part2Flag 1 0 --part3Flag 1 0 --part4Flag 1 0 --blocksPerSegment
  64 -of 0} \\    
		
This execution will generate a file (compilant with the
Recommendation) called \emph{sar16bit.raw.rec}. The wavelet employed
is the integer 9/7, each segment contains 64 blocks and only the first
segment contains the part 2, 3 and 4 header. All other segments have
only Part1 header. To decompress the file and recover the original
image run: 

\emph{\#./TERdecode -i workDir/sar16bit.raw.rec -g 1 512 512 2 0 0 -o
  workDir/sar16bit.raw.rec.raw} 


\vspace{0.25cm}\textbf{LOSSY COMPRESSION}\vspace{0.25cm}

\emph{\#TERcode -i workDir/foc.raw -g 1 512 1024 2 0 0 --pixelBitDepth
  12 - --blocksPerSegment 128 wt 3 -o workDir/foc.raw.rec -of 1}

This exection uses the float 9/7 wavelet transform, then some loss is
produce when coefficients are transformed. To decompress the file and
recover the original image run:

\emph{\#TERdecode -i workDir/foc.raw.rec -o workDir/foc.raw.rec.raw
  -g 1 512 1024 2 0 0}  


\vspace{0.25cm}\textbf{COMPRESSION USING A FIXED SEGBYTELIMIT}\vspace{0.25cm}  

\emph{\#./TERcode -i workDir/sar16bit.raw -g 1 512 512 2 0 0 -wt 4 --part2Flag
1 0 --part3Flag 1 0 --part4Flag 1 0 --blocksPerSegment 64
 -of 0 --segByteLimit 3072 --useFill 1}

This execution creates a file where each segment size is limited to
3072 bytes, in case the size of the segment in lower that 3072, it is
completed with zeros up to the required size. To decompress
the file and recover the original image run:

\emph{\#./TERdecode -i workDir/sar16bit.raw.rec -g 1 512 512 2 0 0 -o
  workDir/sar16bit.raw.rec.raw} 

\vspace{0.25cm}\textbf{COMPRESSION USING CUSTOM WEIGHTS}\vspace{0.25cm} 

\emph{\#TERcode -i workDir/marstest.raw -g 1 512 512 1 0 0 -wt 4
  --part2Flag 1 0 --part3Flag 1 0 --part4Flag 1 0 --blocksPerSegment
  64 --pixelBitDepth 8 -of 0 -wg 1 -cw 4 4 4 2 2
  2 1 1 1 1} 

This execution produces a encoded file with the scaling factor for
each subband of the transformed image given by the user. To decompress
the file and recover the original image run:

\emph{\#TERdecode -i workDir/marstest.raw.rec -o
  workDir/marstest.raw.rec.raw -g 1 512 512 1 0 0} 

\vspace{0.25cm}\textbf{ONLY DC COMPONENTS COMPRESSION}\vspace{0.25cm}
\emph{\#TERcode -i workDir/marstest.raw -g 1 512 512 1 0 0 -o
workDir/temp.coded -of 0 -wt 4 --blocksPerSegment 64 --part2Flag 1 0
--part3Flag 1 0 --part4Flag 1 0 -dc 1}

This execution produces a encoded file where only DC components are
encoded. To decompress the file and recover the original image run:

\emph{\#TERdecode -i workDir/temp.coded.rec -o
  workDir/marstest.raw.rec.raw -g 1 512 512 1 0 0} 

\vspace{0.25cm}\textbf{COMPRESSION UP TO A FIXED BITPLANE AND
  STAGE}\vspace{0.25cm}   

\emph{\#TERcode -i workDir/marstest.raw -g 1 512 512 1 0 0 -o
workDir/marstest.raw -of 0 -wt 4 --blocksPerSegment 64 --part2Flag 1 0
--part3Flag 1 0 --part4Flag 1 0 -dc 0 -bp 1 -ss 2}

This execution produces a encoded file that each segment is encoded up
to the bit plane 1 and the stage 2. To decompress
the file and recover the original image run:

\emph{\#TERdecode -i workDir/marstest.raw.rec -g 1 512 512 1 0 0 -o
workDir/marstest.raw.rec.raw}

\vspace{0.25cm}\textbf{COMPRESSION USING A DIFFERENT ANY NUMBER OF
  WAVELET LEVELS}\vspace{0.25cm}  

\emph{\#TERcode -i workDir/lena.pgm -wl 5 -wt 3 -o
  workDir/lena.pgm -of 1 -po 0}

This execution produces a file,  workDir/lena.pgm.ter,
that is not compilant with the Recommendation.
To decompress the file and recover the original image run:

\emph{\#TERcode -i workDir/lena.pgm.ter -o
  workDir/lena.pgm.ter.pgm}

\vspace{0.25cm}\textbf{SHOWING COMPRESSION
  STATISTICS}\vspace{0.25cm} 

In some cases it is interesting to show the time that each stage
lasts and the used memory. It can be done by: 

\emph{\#TERcode -i inputImage.pgm -o outputFile -vc 1} \\ 

\end{document}
